### 2021-05-06 article/article.tex
update

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Methodology}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. %TODO: add more here?

@@

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.

@@

\section{Results}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:ICchisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.

@@

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_ett.pdf}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_emt.pdf}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eem.pdf}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eet.pdf}
    \end{center}
    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all NSI 
    parameters not shown in each plot are set to zero.}\label{fig:PINGU_3D}
 \end{figure}

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
    \end{center}
    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
 \end{figure}

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
\begin{align}
    \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
\end{align}
with test statistic $\chi^2_\text{joint,min}$.

\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/emm_deltachi.pdf}
    \end{center}
    \caption{}\label{fig:emm_deltachi}
 \end{figure}

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
    \end{center}
    \caption{}\label{fig:emm_emp_contour}
 \end{figure}
%At $90\%$ CL:
%PINGU: $-0.046 < \emm < 0.041$
%DC: $-0.045 < \emm < 0.041$
%joint: $-0.038 < \emm < 0.033$

%TODO: table with individual and combined chisq values. Discussion on impact of IC on chisq.

>>>>

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Methodology}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. %TODO: add more here? no neutrino absorption

@@

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{SI}$ $(N_{NSI})$ are the numbers of expected events
assuming standard (non-standard) interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.

@@

\section{Results}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.

@@

\begin{figure}[!tb]
   \begin{center}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_3D_NO.pdf}
         \label{fig:PINGU_3D_NO}
         \caption{PINGU}
      \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_3D_NO.pdf}
         \label{fig:PINGU_3D_NO}
         \caption{DeepCore}
      \end{subfigure}
    \end{center}
    \caption{Minimization of the $\Delta \chi^2$ defined in Eq.~\ref{eq:chisq} after three years of data.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than the one displayed in each panel are set to zero.}\label{fig:3D_NO}
 \end{figure}

 \begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 3 - 5 } Parameter & 90\% CL\hspace{1cm} & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ & -0.028, 0.044\hspace{1cm} & 2.435 & 47.84 & 0.0125 \\
           $\emt$ & -0.015, 0.0050\hspace{1cm} & 2.435 & 43.97 & -0.005 \\
           $\eem$ & -0.068, 0.070\hspace{1cm} & 2.435 & 43.97 & 0 \\
           $\eet$ & -0.072, 0.14\hspace{1cm} & 2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} PINGU } \\
           $\ett$ & -0.036, -\hspace{1cm} & 2.517 & 49.2 & 0 \\
           $\emt$ & -0.0076, 0.0085\hspace{1cm} & 2.517 & 49.2 & 0\\
           $\eem$ & -0.060, 0.055\hspace{1cm} & 2.517 & 49.2 & 0 \\
           $\eet$ & -0.065, 0.072\hspace{1cm} & 2.517 & 49.2 & 0 \\
           \hline
           \hline
       \label{table:DC_PINGU_results}
   \end{tabular}
   \end{center}
   \caption{DeepCore and PINGU results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}
\end{table}

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
\begin{align}\label{eq:joint_chisq}
    \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
\end{align}
with test statistic $\chi^2_\text{joint,min}$.

\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/joint_3D_NO.pdf}
    \end{center}
    \caption{Minimization of the joint $\chi^2$ from Eq.~\ref{fig:joint_chisq} using the $\Delta \chi^2$ shown in Fig.~\ref{fig:3D_NO}}
    \label{fig:joint_3D}
 \end{figure}

 \begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 3 - 5 } Parameter & 90\% CL\hspace{1cm} & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline
           $\ett$ & -0.029, 0.0473\hspace{1cm} & 2.489 & 47.84 & 0.0125\\
           $\emt$ & -0.0063, 0.0050\hspace{1cm} & 2.489 & 47.84 & 0\\
           $\eem$ & -0.046, 0.046 \hspace{1cm} & 2.489 & 47.84 & 0 \\
           $\eet$ & -0.057, 0.028 \hspace{1cm} & 2.489 & 47.84 & 0 \\
           \hline
       \label{table:joint_results}
   \end{tabular}
   \end{center}
   \caption{Joint results from $\chi^2_\{text}$ defined in Eq.~\ref{eq:joint_chisq}. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}
\end{table}

%TODO:  Discussion on impact of IC on chisq.?
